### 2025-05-08 project2/nnMetamodels.tex
new

\gls{dnn} have attracted attentions of researchers and practitioners due to their success~\citep{hastie2009elements,lecun2015deep} in solving real-world machine learning tasks such as AlphaGo~\citep{silver2016mastering} and ChatGPT~\citep{chatgpt}.
Since the first artificial neural network model~\citep{mcculloch1943logical} and the first algorithm for training a perceptron~\citep{rosenblatt1958perceptron}, especially after the introduction of backpropagation~\citep{rumelhart1985learning} and the growth of high-performance computing, the field of artificial neural network and deep learning in general has been growing rapidly.
Two specialized neural network architectures that are relevant to our study are \gls{rnn}~\citep{williams1989learning,sutskever2014sequence} and \gls{lstm}~\citep{hochreiter1997long,chung2014empirical}.
Despite their success, \gls{dnn} models are often criticized for their lack of transparency and interpretability, which hinders their adoption in financial and actuarial applications.
Enormous research efforts have been spent to test and improve the robustness of \gls{dnn} models with carefully designed noise injection methods.
~\cite{poole2014analyzing} show that injecting synthetic noise before and after hidden unit activations during training improves the performance of autoencoders.
~\cite{neelakantan2015adding} improve learning for \gls{dnn}s by injecting synthetic noise to the gradients during backpropagations.
A branch of research has been devoted to understanding the resilience of neural network models to noise in training labels.
For example,~\cite{luo2016understanding} show that adding synthetic label noise to the convolutional neural network (\gls{cnn}) can improve its ability to capture global features. 
~\cite{srivastava2014dropout} quantify the error tolerance by injecting synthetic label noise with a custom Boltzmann machine hardware.
~\cite{szegedy2013intriguing} find that neural networks are vulnerable to adversarial examples, and~\cite{goodfellow2014explaining} design an efficient method to generate such noisy examples to exploit the vulnerability to adversarial perturbations.
~\cite{carlini2017towards} design targeted attacks to training labels to test the robustness of neural networks. 
Instead of using synthetic noise, ~\cite{jiang2020beyond} inject real-world label noise and examine noise tolerance of neural networks with controlled noise levels.
The aforementioned studies use real-world data, as is typically the case for many neural network studies, where noise is already present in the training labels before any noise injection.
Users of real-world data have little control over the noise level of the original training labels and usually examine the effect of noisy data by injecting noise, but it is unclear whether a neural network model trained on noisy data actually learns the real, i.e., noiseless, feature-label relationship.
Due to their lack of transparency and interpretability, the adoption of \gls{dnn}s in financial and actuarial applications has been received by regulators with some skepticism.

@@

Estimating tail risk measures of portfolios of complex \gls{va}s usually requires nested simulation.
In the nested simulation, the outer simulation involves projecting scenarios of key risk factors under a $\mathbb{P}$ measure, while the inner simulations are used to value payoffs uder guarantees of varying complexity, under a $\mathbb{Q}$ measure.

@@

In Chapter~\ref{chap:project1}, the likelihood ratio approach is used to allocate the inner simulation budget using likelihood ratio weights, i.e., importance sampling.
Proxy models are tractable analytic functions or flexible empirical functions that are used to replace the inner simulation stage of a nested simulation.
Empirical proxies may be intrinsic or extrinsic to the simulation process. Extrinsic proxy functions are selected to be close to the inner simulation values and therefore require detailed information about the payoffs that are evaluated in the inner simulation step. 
Empirical proxies are constructed by using an initial pilot simulation to develop factors or functionals that can subsequently be used in place of the inner simulation. 
A prominent expirical proxy method discussed in the literature is the least squares Monte Carlo method~\citep{longstaff2001valuing}.
In Chapter~\ref{chap:project1}, supervised learning models, including linear regression, \gls{knn}, and \gls{krr}, are used as proxy models for inner simulations.
This chapter introduces a proxy model to reduce the computational requirements of inner simulations of \gls{va}s by replacing the inner simulation step of a nested simulation procedure. 
This proxy model is chosen to be a flexible empirical function, i.e., a \gls{dnn} metamodel.

In our study, supervised learning metamodels are trained using data simulated from an initial pilot simulation.
They are then used to replace the time-consuming inner simulations by the trained model.
Borrowing terminologies from the machine learning community, we can view a set of simulated outer scenarios and estimated hedging errors for those scenarios as \textit{features} and noisy \textit{labels}.
The noise level of the labels can be controlled by the number of inner replications in the inner simulation model.
We refer to the trained supervised learning proxy models as \textit{metamodels} of the inner simulation, which is also known as the \textit{surrogate models} in the simulation literature.
Metamodeling is a popular approach to reduce the computational burden of simulation-based applications by replacing the time-consuming simulation with a metamodel.
The metamodel is trained using a set of simulated data, and it is used to predict the simulation output for new inputs.
The study of metamodeling is an active research area in the simulation literature, and using \gls{dnn}s as metamodels is a relatively new development.
~\cite{fonseca2003simulation} provide general guidelines for simulation metamodeling with neural networks,~\cite{lieu2022adaptive} use \gls{dnn}s as metamodels of a simulation model for a structural reliability analysis, and~\cite{salle2014efficient} show that neural network metamodels help achieve higher degree of prediction accuracy that other metamodels in approximating agent-based simulation models.
A popular metamodel in nested simulation procedures is stochastic kriging.
~\cite{liu2010stochastic} use stochastic kriging as a metamodel of Monte Carlo simulations to estimate the \gls{cvar} of a portfolio of derivative securities, and~\cite{gan2015valuation} use a stochastic kriging for an efficient valuation of large portfolios of \gls{va} contracts.
Other studies, such as ~\cite{broadie2015risk},~\cite{hong2017kernel}, and~\cite{zhang2022sample} use a regression, a kernel smoothing, and a likelihood ratio method, respectively as metamodels.
Our study has three key distinctions over the existing ones:
\begin{enumerate}
    \item  our metamodel has high-dimensional inputs. In machine learning terminology, the features are high-dimensional vectors.
    To estimate the hedging error of a typical \gls{va} contract, the number of features is in the order of hundreds, which is at least one order of magnitude larger than the number of features in the aforementioned studies,
    \item  for estimating tail risk measures, our metamodel is only used for tail scenario identification but is \textit{not} used in the estimation of the tail risk measures.
    This is a feature designed particularly to convince regulators that the losses used in estimating the risk measure are based on a transparent inner simulation model rather than on some black-box metamodels, and
    \item  using simulation models as data generators, we can decrease the noise level and get arbitrarily close to the true labels by increasing the number of replications in the simulation model.
    This design allows a systematic study of the effect of noisy training labels on the performance of \gls{dnn} models in predicting the noiseless labels.
\end{enumerate}

@@

The rest of this chapter is organized as follows.
Section~\ref{sec2:problem-formulation} presents the problem settings for tail risk measures and dynamic hedging of \gls{va}s. 
Section~\ref{sec2:metamodel2Stage} proposes an efficient two-stage nested simulation procedure that uses \gls{dnn}s as metamodels to help reduce a simulation budget by only performing computations on identified tail scenarios. 
Section~\ref{sec2:metamodel1Stage} proposes a single-stage nested simulation procedure that estimates risk measures directly with metamodel predictions.
Section~\ref{sec2:numerical} demonstrates the efficiency of \gls{dnn} metamodels and examines the error tolerance of two \gls{lstm} metamodels with different numbers of trainable parameters. 
Lastly, practical suggestions are provided for the choice of suitable metamodels and simulation settings.

@@

In this section we present notations, problem settings, and a simulation model for risk estimation for hedging errors of \gls{va}s.
A main goal of this section is to showcase the complexity of the simulation model, which we use as a data generator to train \gls{dnn} metamodels (Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage}).
For readers who are interested in the examination of a neural network metamodel, it is sufficient to understand that our simulation model generates data with 240 features and 1 real-value label and our metamodels are generally applicable to any simulation model that generates data with similar characteristics.

@@

Consider a loss random variable $L$ which losses and gains lie in the right and left tails, respectively, of its distribution.
For a given confidence level $\alpha\in [0,1]$, the $\alpha$-\gls{var} and $\alpha$-\gls{cvar} are defined in Equation~\eqref{eq1:var} and Equation~\eqref{eq1:cvar}, respectively.
Tail risk measures such as \gls{var} and \gls{cvar} are widely used for setting a regulatory and economic capital, which is the amount of capital a financial institution holds to cover its risk.
For example, European insurers set regulatory capital at $99.5\%$-\gls{var} according to Solvency II~\cite{eiopa2014underlying}.
In Canada, the regulatory capital requirement for \gls{va}s is set based on \gls{cvar}s as prescribed in~\cite{osfi2017life}.

@@

\begin{algorithm} 
\caption{Standard Nested Simulation Procedure for Estimating CVaR for GMWB Hedging Losses}
\begin{algorithmic}[1] \label{alg2:standardProcedure}
    \STATE  For $i=1,\ldots,M$, simulate outer scenarios $\bS^{(i)} = (S_{1}^{(i)},\ldots,S_{T}^{(i)})$ under the real-world measure $\mathbb{P}$.
    \STATE  For $t=0$, simulate time-$0$ inner paths $\bStilde_{0}^{(j)} = (\Stilde_{1}^{(j)},\Stilde_{2}^{(j)},\ldots,\Stilde_{T}^{(j)})$, $j=1,\ldots,N$ under $\mathbb{Q}$, then estimate $V_0$ by $\Vhat_0 = \sum_{s=1}^{T} e^{-r(T-s)} [(I_s - F_s)^+- \eta_n F_s]$ and $\Deltahat_0 = \Delta_0(\Stilde_{1}^{(j)},\ldots,\Stilde_{T}^{(j)} | S_0)$.
    \STATE  Given each scenario $\bS^{(i)}$:
    \begin{enumerate}[label=\alph*., itemsep=0pt, parsep=0pt, topsep=0pt]
        \item   At each time~$t=1,\ldots,T-1$, simulate inner paths $\bStilde_{t}^{(ij)} = (\Stilde_{t+1}^{(ij)},\ldots,\Stilde_{T}^{(ij)})$, $j=1,\ldots,N$ under $\mathbb{Q}$, then estimate $\Delta_t$ by $\Deltahat_t^{(i)} = \Delta_t(\Stilde_{t+1}^{(ij)},\ldots,\Stilde_{T}^{(ij)} | \bm{S}_t^{(i)})$.
        \item   Use scenarios $\bS^{(i)}$ and $\Vhat_0$ and $\Deltahat_t^{(i)}$ to calculate losses $\Lhat_i^{MC}$, $t=0,\ldots,T-1$, then sort them as $\Lhat^{MC}_{(1)}\leq \Lhat^{MC}_{(2)} \leq \cdots\leq \Lhat^{MC}_{(M)}$.
    \end{enumerate}
    \STATE  Estimate $\alpha$-CVaR of $L$ by $\widehat{\CVaR}^{MC}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}\Lhat_{(i)}^{MC} = \frac{1}{(1-\alpha)M} \sum_{i \in \widehat{\tail}_{(1-\alpha )M}^{MC}}\Lhat_{i}^{MC}$.
\end{algorithmic}
\end{algorithm}

We refer to the collection of experiments needed conditional on one scenario $\bS^{(i)}$ to estimate $L_i$, which is all upward arrows in Figure~\ref{fig2:illustration}, as one inner simulation.
We make four observations:
\begin{itemize}
    \item   Each inner simulation is time-consuming, as it includes $T$ simulation experiments: one at each time $t=0,\ldots,T-1$,
    \item   After running inner simulations for $M$ scenarios, we obtain simulated data as feature-label pairs, $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$; the feature vector $\bS$ is $T$ dimensional.
    \item   $\Lhat_i^{MC}$ is a standard Monte Carlo estimator of the true loss for scenario $\bS^{(i)}$. 
    It is an unbiased estimator and its variance is inversely proportional to the number of inner replications $N$. 
    As $N$ approaches infinity, $\Lhat_i^{MC}$ converges to the true loss $L_i$, and
    \item   Most importantly, when estimating tail risk measures such as $\alpha$-\gls{cvar}, only a small number of estimated losses, which is those associated with the set of tail scenarios $\widehat{\tail}_{k}$ are used in the estimator.
\end{itemize}

@@

We conduct a series of simulation experiments to 
\begin{enumerate}
    \item demonstrate the efficiency of the proposed metamodeling procedures, and
    \item examine the error tolerance to noisy training data in deep learning models.
\end{enumerate}
The problem settings in our experiments are identical to those in~\cite{dang2020efficient}.
We consider estimating the $95\%$ \gls{cvar} of the hedging loss of a \gls{gmwb} contract, which is one of the most complex \gls{va} contracts in the market.
The \gls{va} contracts have a 20-year maturity and are delta-hedged with monthly rebalancing, i.e., $T=240$ rebalancing periods.
The gross and net management fees are $\eta_g = 0.2\%$ and $\eta_n=0.1\%$, respectively.
The withdrawal rate for \gls{gmwb} is $0.375\%$ per month.
To make our examples more realistic, the \gls{va}s are also subject to a dynamic lapse model with the following key features~\citep{naic2021}:
\begin{enumerate}
    \item When a policyholder lapses, both the fund value ($F$) and guarantee value ($G$) are reduced proportionally.
    \item The monthly lapse rate from time $t$ to $t + 1$, denoted as ${}_{\frac{1}{12}}q^l_{x+\frac{t}{12}}$, is given by:
    \begin{equation} \label{eq:dynamic_lapse_rate}
        {}_{\frac{1}{12}}q^l_{x+\frac{t}{12}} = \min\left\{1, \max\left\{0.5, 1 - 1.25 \times \left(\frac{G_t}{F_t} - 1.1\right)\right\} \times {}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}}\right\}
    \end{equation}
    where ${}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}}$ is a base monthly mortality rate for a policyholder aged $x + \frac{t}{12}$ at month $t$, and the base monthly lapse rate is defined as:
    \begin{equation} \label{eq:lapse_rate}
        {}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}} = 
        \begin{cases}
            0.00417 & \text{if } t < 84, \\
            0.00833 & \text{if } t \geq 84.
        \end{cases}
    \end{equation}
\end{enumerate}

@@

Five metamodels are considered in this experiment: \gls{mlr}, \gls{qpr} without interaction terms, \gls{fnn}, \gls{rnn}, and \gls{lstm} network.
\gls{mlr} and \gls{qpr} are two common metamodels in the simulation literature, and their implemention is straightfoward in our simulation setting.
\gls{fnn} is a generic neural network while \gls{rnn} and \gls{lstm} are specialized models to accommodate the sequential structure of our time-series features.
A $\tanh$ activation function is used for \gls{rnn} and \gls{lstm} layers, and a ReLU activation function is used for the fully-connected layers.
All neural network metamodels are trained by the Adam optimizer~\citep{kingma2014adam} with an initial learning rate of $0.001$ and an exponential learning rate decay schedule.
All \gls{dnn} metamodels are trained with a dropout rate of $10\%$.
The architectures and training settings are typical choices in the deep learning literature.
The training labels are normalized to have a zero mean and a unit standard deviation.
The numbers of trainable parameters are recorded in the second column of Table~\ref{tab:gmwb_arch}.
We observe that the three \gls{dnn} metamodels have orders of magnitudes more trainable parameters than the two traditional regression metamodels.
Following the convention in machine learning literature, the three \gls{dnn} metamodels are said to have much higher \textit{model capacities}.
Treating regression metamodels as shallow neural networks, \gls{mlr} and \gls{qpr} are two neural networks with no hidden layer. 
For a traditional regression metamodel, the numbers of neurons in its input layer equals to the cardinality of its regression basis.
On the other hand, the three \gls{dnn} metamodels have several hidden layers and are more flexible than \gls{mlr} and \gls{qpr}.
Our \gls{fnn} has two hidden layers prior to its output layer.
Its hidden layers are feature extraction layers that transform the 240-dimension feature vector into a 32-dimension vector that can directly relate to the target variable.
This extraction process is automatic and does not require manual feature engineering.
Our \gls{rnn} and \gls{lstm} networks have three hidden layers.
They contain similar numbers of neurons as the \gls{fnn} but have deeper network structures.
For \gls{rnn}, two of its hidden layers are recurrent layers that capture the temporal dependency in the feature, and its last hidden layer is a standard feedforward layer that transforms the previous hidden states into a 32-dimension vector for target prediction.
Our \gls{lstm} has the same architecture as the \gls{rnn} but with \gls{lstm} cells in place of \gls{rnn} cells.

@@

For financial and actuarial applications, regulators and practitioners are often concerned about the robustness of \gls{dnn} models to noise in training labels, which hinders the adoption of these models in practice.
Since the true relationship is unknown in real-world applications, most deep learning literature illustrates the impact of noise by artificially injecting noise into real-world datasets, which is already noisy prior to the injection.
In our numerical experiments, we are able to use Monte Carlo simulation to generate a true dataset that approximates the true hedging losses with a high degree of precision, and, as a result, we are able to explore the important question of whether deep learning models are indeed capable of learning the true feature-label relationship from noisy training labels.
In this section, we treat the standard nested simulation procedure as a data generator and examine the noise tolerance of \gls{lstm} metamodels by varying the numbers of the outer scenarios ($M$) and the inner replications ($N$) used to generate the training samples.

@@

Our novel experiment design allows us to examine the impact of label noise on \gls{dnn} models.
We find that a \gls{dnn} with a suitable architecture is able to cut through the noise in training labels and learn the true complex dynamic hedging model.
By showcasing the resilience of these models, our study aims at encouraging regulatory bodies to recognize the value and applicability of deep learning metamodels in financial risk management, and it provides informed suggestions and guidance for the incorporation and oversight of advanced deep learning metamodel in Monte Carlo Simulation in financial applications.
Our findings are particularly insightful in this context.

>>>>

\gls{dnn} have attracted attentions of researchers and practitioners due to their success~\citep{hastie2009elements,lecun2015deep} in solving real-world machine learning tasks such as AlphaGo~\citep{silver2016mastering} and ChatGPT~\citep{chatgpt}.
Since the first artificial neural network model~\citep{mcculloch1943logical} and the first algorithm for training a perceptron~\citep{rosenblatt1958perceptron}, especially after the introduction of backpropagation~\citep{rumelhart1985learning} and the growth of high-performance computing, the field of artificial neural network and deep learning in general has been growing rapidly.
Two specialized neural network architectures that are relevant to our study are \gls{rnn}~\citep{williams1989learning,sutskever2014sequence} and \gls{lstm}~\citep{hochreiter1997long,chung2014empirical}.
Despite their success, \gls{dnn} models are often criticized for their lack of transparency and interpretability, which hinders their adoption in financial and actuarial applications.
Enormous research efforts have been spent to test and improve the robustness of \gls{dnn} models with carefully designed noise injection methods.
~\cite{poole2014analyzing} show that injecting synthetic noise before and after hidden unit activations during training improves the performance of autoencoders.
~\cite{neelakantan2015adding} improve learning for \gls{dnn}s by injecting synthetic noise to the gradients during backpropagations.
A branch of research has been devoted to understanding the resilience of neural network models to noise in training labels.
For example,~\cite{luo2016understanding} show that adding synthetic label noise to the \gls{cnn} can improve its ability to capture global features. 
~\cite{srivastava2014dropout} quantify the error tolerance by injecting synthetic label noise with a custom Boltzmann machine hardware.
~\cite{szegedy2013intriguing} find that neural networks are vulnerable to adversarial examples, and~\cite{goodfellow2014explaining} design an efficient method to generate such noisy examples to exploit the vulnerability to adversarial perturbations.
~\cite{carlini2017towards} design targeted attacks to training labels to test the robustness of neural networks. 
Instead of using synthetic noise, ~\cite{jiang2020beyond} inject real-world label noise and examine noise tolerance of neural networks with controlled noise levels.
The aforementioned studies use real-world data, as is typically the case for many neural network studies, where noise is already present in the training labels before any noise injection.
Users of real-world data have little control over the noise level of the original training labels and usually examine the effect of noisy data by injecting noise, but it is unclear whether a neural network model trained on noisy data actually learns the real, i.e., noiseless, feature-label relationship.
Due to their lack of transparency and interpretability, the adoption of \gls{dnn}s in financial and actuarial applications has been received by regulators with some skepticism.

@@

Estimating tail risk measures of portfolios of complex \gls{va} contracts usually requires nested simulation.
In the nested simulation, the outer simulation involves projecting scenarios of key risk factors under a $\mathbb{P}$ measure, while the inner simulations are used to value payoffs uder guarantees of varying complexity, under a $\mathbb{Q}$ measure.

@@

In Chapter~\ref{chap:project1}, the likelihood ratio approach is used to allocate the inner simulation budget using likelihood ratio weights, i.e., importance sampling.
Proxy models are tractable analytic functions or flexible empirical functions that are used to replace the inner simulation stage of a nested simulation.
Empirical proxies may be intrinsic or extrinsic to the simulation process. Extrinsic proxy functions are selected to be close to the inner simulation values and therefore require detailed information about the payoffs that are evaluated in the inner simulation step. 
Empirical proxies are constructed by using an initial pilot simulation to develop factors or functionals that can subsequently be used in place of the inner simulation. 
A prominent expirical proxy method discussed in the literature is the least squares \gls{mc} method~\citep{longstaff2001valuing}.
In Chapter~\ref{chap:project1}, supervised learning models, including linear regression, \gls{knn}, and \gls{krr}, are used as proxy models for inner simulations.
This chapter introduces a proxy model to reduce the computational requirements of inner simulations of \gls{va} contracts by replacing the inner simulation step of a nested simulation procedure. 
This proxy model is chosen to be a flexible empirical function, i.e., a \gls{dnn} metamodel.

In our study, supervised learning metamodels are trained using data simulated from an initial pilot simulation.
They are then used to replace the time-consuming inner simulations by the trained model.
Borrowing terminologies from the machine learning community, we can view a set of simulated outer scenarios and estimated hedging errors for those scenarios as \textit{features} and noisy \textit{labels}.
The noise level of the labels can be controlled by the number of inner replications in the inner simulation model.
We refer to the trained supervised learning proxy models as \textit{metamodels} of the inner simulation, which is also known as the \textit{surrogate models} in the simulation literature.
Metamodeling is a popular approach to reduce the computational burden of simulation-based applications by replacing the time-consuming simulation with a metamodel.
The metamodel is trained using a set of simulated data, and it is used to predict the simulation output for new inputs.
The study of metamodeling is an active research area in the simulation literature, and using \gls{dnn}s as metamodels is a relatively new development.
~\cite{fonseca2003simulation} provide general guidelines for simulation metamodeling with neural networks,~\cite{lieu2022adaptive} use \gls{dnn}s as metamodels of a simulation model for a structural reliability analysis, and~\cite{salle2014efficient} show that neural network metamodels help achieve higher degree of prediction accuracy that other metamodels in approximating agent-based simulation models.
A popular metamodel in nested simulation procedures is stochastic kriging.
~\cite{liu2010stochastic} use stochastic kriging as a metamodel of \gls{mc} simulations to estimate the \gls{cvar} of a portfolio of derivative securities, and~\cite{gan2015valuation} use a stochastic kriging for an efficient valuation of large portfolios of \gls{va} contracts.
Other studies, such as ~\cite{broadie2015risk},~\cite{hong2017kernel}, and~\cite{zhang2022sample} use a regression, a kernel smoothing, and a likelihood ratio method, respectively as metamodels.
Our study has three key distinctions over the existing ones:
\begin{enumerate}
    \item  our metamodel has high-dimensional inputs. In machine learning terminology, the features are high-dimensional vectors.
    To estimate the hedging error of a typical \gls{va} contract, the number of features is in the order of hundreds, which is at least one order of magnitude larger than the number of features in the aforementioned studies,
    \item  for estimating tail risk measures, our metamodel is only used for tail scenario identification but is \textit{not} used in the estimation of the tail risk measures.
    This is a feature designed particularly to convince regulators that the losses used in estimating the risk measure are based on a transparent inner simulation model rather than on some black-box metamodels, and
    \item  using simulation models as data generators, we can decrease the noise level and get arbitrarily close to the true labels by increasing the number of replications in the simulation model.
    This design allows a systematic study of the effect of noisy training labels on the performance of \gls{dnn} models in predicting the noiseless labels.
\end{enumerate}

@@

The rest of this chapter is organized as follows.
Section~\ref{sec2:problem-formulation} presents the problem settings for tail risk measures and dynamic hedging of \gls{va} contracts. 
Section~\ref{sec2:metamodel2Stage} proposes an efficient two-stage nested simulation procedure that uses \gls{dnn}s as metamodels to help reduce a simulation budget by only performing computations on identified tail scenarios. 
Section~\ref{sec2:metamodel1Stage} proposes a single-stage nested simulation procedure that estimates risk measures directly with metamodel predictions.
Section~\ref{sec2:numerical} demonstrates the efficiency of \gls{dnn} metamodels and examines the error tolerance of two \gls{lstm} metamodels with different numbers of trainable parameters. 
Lastly, practical suggestions are provided for the choice of suitable metamodels and simulation settings.

@@

In this section we present notations, problem settings, and a simulation model for risk estimation for hedging errors of \gls{va} contracts.
A main goal of this section is to showcase the complexity of the simulation model, which we use as a data generator to train \gls{dnn} metamodels (Section~\ref{sec2:metamodel2Stage} and Section~\ref{sec2:metamodel1Stage}).
For readers who are interested in the examination of a neural network metamodel, it is sufficient to understand that our simulation model generates data with 240 features and 1 real-value label and our metamodels are generally applicable to any simulation model that generates data with similar characteristics.

@@

Consider a loss random variable $L$ which losses and gains lie in the right and left tails, respectively, of its distribution.
For a given confidence level $\alpha\in [0,1]$, the $\alpha$-\gls{var} and $\alpha$-\gls{cvar} are defined in Equation~\eqref{eq1:var} and Equation~\eqref{eq1:cvar}, respectively.
Tail risk measures such as \gls{var} and \gls{cvar} are widely used for setting a regulatory and economic capital, which is the amount of capital a financial institution holds to cover its risk.
For example, European insurers set regulatory capital at $99.5\%$-\gls{var} according to Solvency II~\cite{eiopa2014underlying}.
In Canada, the regulatory capital requirement for \gls{va} contracts is set based on \gls{cvar}s as prescribed in~\cite{osfi2017life}.

@@

\begin{algorithm} 
\caption{Standard Nested Simulation Procedure for Estimating CVaR for \gls{gmwb} Hedging Losses}
\begin{algorithmic}[1] \label{alg2:standardProcedure}
    \STATE  For $i=1,\ldots,M$, simulate outer scenarios $\bS^{(i)} = (S_{1}^{(i)},\ldots,S_{T}^{(i)})$ under the real-world measure $\mathbb{P}$.
    \STATE  For $t=0$, simulate time-$0$ inner paths $\bStilde_{0}^{(j)} = (\Stilde_{1}^{(j)},\Stilde_{2}^{(j)},\ldots,\Stilde_{T}^{(j)})$, $j=1,\ldots,N$ under $\mathbb{Q}$, then estimate $V_0$ by $\Vhat_0 = \sum_{s=1}^{T} e^{-r(T-s)} [(I_s - F_s)^+- \eta_n F_s]$ and $\Deltahat_0 = \Delta_0(\Stilde_{1}^{(j)},\ldots,\Stilde_{T}^{(j)} | S_0)$.
    \STATE  Given each scenario $\bS^{(i)}$:
    \begin{enumerate}[label=\alph*., itemsep=0pt, parsep=0pt, topsep=0pt]
        \item   At each time~$t=1,\ldots,T-1$, simulate inner paths $\bStilde_{t}^{(ij)} = (\Stilde_{t+1}^{(ij)},\ldots,\Stilde_{T}^{(ij)})$, $j=1,\ldots,N$ under $\mathbb{Q}$, then estimate $\Delta_t$ by $\Deltahat_t^{(i)} = \Delta_t(\Stilde_{t+1}^{(ij)},\ldots,\Stilde_{T}^{(ij)} | \bm{S}_t^{(i)})$.
        \item   Use scenarios $\bS^{(i)}$ and $\Vhat_0$ and $\Deltahat_t^{(i)}$ to calculate losses $\Lhat_i^{MC}$, $t=0,\ldots,T-1$, then sort them as $\Lhat^{MC}_{(1)}\leq \Lhat^{MC}_{(2)} \leq \cdots\leq \Lhat^{MC}_{(M)}$.
    \end{enumerate}
    \STATE  Estimate $\alpha$-CVaR of $L$ by $\widehat{\CVaR}^{MC}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}\Lhat_{(i)}^{MC} = \frac{1}{(1-\alpha)M} \sum_{i \in \widehat{\tail}_{(1-\alpha )M}^{MC}}\Lhat_{i}^{MC}$.
\end{algorithmic}
\end{algorithm}

We refer to the collection of experiments needed conditional on one scenario $\bS^{(i)}$ to estimate $L_i$, which is all upward arrows in Figure~\ref{fig2:illustration}, as one inner simulation.
We make four observations:
\begin{itemize}
    \item   Each inner simulation is time-consuming, as it includes $T$ simulation experiments: one at each time $t=0,\ldots,T-1$,
    \item   After running inner simulations for $M$ scenarios, we obtain simulated data as feature-label pairs, $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$; the feature vector $\bS$ is $T$ dimensional.
    \item   $\Lhat_i^{MC}$ is a standard \gls{mc} estimator of the true loss for scenario $\bS^{(i)}$. 
    It is an unbiased estimator and its variance is inversely proportional to the number of inner replications $N$. 
    As $N$ approaches infinity, $\Lhat_i^{MC}$ converges to the true loss $L_i$, and
    \item   Most importantly, when estimating tail risk measures such as $\alpha$-\gls{cvar}, only a small number of estimated losses, which is those associated with the set of tail scenarios $\widehat{\tail}_{k}$ are used in the estimator.
\end{itemize}

@@

We conduct a series of simulation experiments to 
\begin{enumerate}
    \item demonstrate the efficiency of the proposed metamodeling procedures, and
    \item examine the error tolerance to noisy training data in deep learning models.
\end{enumerate}
The problem settings in our experiments are identical to those in~\cite{dang2020efficient}.
We consider estimating the $95\%$ \gls{cvar} of the hedging loss of a \gls{gmwb} contract, which is one of the most complex \gls{va} contracts in the market.
The \gls{va} contracts have a 20-year maturity and are delta-hedged with monthly rebalancing, i.e., $T=240$ rebalancing periods.
The gross and net management fees are $\eta_g = 0.2\%$ and $\eta_n=0.1\%$, respectively.
The withdrawal rate for \gls{gmwb} is $0.375\%$ per month.
To make our examples more realistic, the \gls{va} contracts are also subject to a dynamic lapse model with the following key features~\citep{naic2021}:
\begin{enumerate}
    \item When a policyholder lapses, both the fund value ($F$) and guarantee value ($G$) are reduced proportionally.
    \item The monthly lapse rate from time $t$ to $t + 1$, denoted as ${}_{\frac{1}{12}}q^l_{x+\frac{t}{12}}$, is given by:
    \begin{equation} \label{eq:dynamic_lapse_rate}
        {}_{\frac{1}{12}}q^l_{x+\frac{t}{12}} = \min\left\{1, \max\left\{0.5, 1 - 1.25 \times \left(\frac{G_t}{F_t} - 1.1\right)\right\} \times {}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}}\right\}
    \end{equation}
    where ${}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}}$ is a base monthly mortality rate for a policyholder aged $x + \frac{t}{12}$ at month $t$, and the base monthly lapse rate is defined as:
    \begin{equation} \label{eq:lapse_rate}
        {}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}} = 
        \begin{cases}
            0.00417 & \text{if } t < 84, \\
            0.00833 & \text{if } t \geq 84.
        \end{cases}
    \end{equation}
\end{enumerate}

@@

Five metamodels are considered in this experiment: \gls{mlr}, \gls{qpr} without interaction terms, \gls{fnn}, \gls{rnn}, and \gls{lstm} network.
\gls{mlr} and \gls{qpr} are two common metamodels in the simulation literature, and their implemention is straightfoward in our simulation setting.
\gls{fnn} (Equation~\refeq{eq:fnn}) is a generic neural network while \gls{rnn} (Equation~\refeq{eq:rnn}) and \gls{lstm} (Equation~\refeq{eq:lstm}) are specialized models to accommodate the sequential structure of our time-series features.
A $\tanh$ activation function is used for \gls{rnn} and \gls{lstm} layers, and a ReLU activation function is used for the fully-connected layers.
All neural network metamodels are trained by the Adam optimizer~\citep{kingma2014adam} with an initial learning rate of $0.001$ and an exponential learning rate decay schedule.
All \gls{dnn} metamodels are trained with a dropout rate of $10\%$.
The architectures and training settings are typical choices in the deep learning literature.
The training labels are normalized to have a zero mean and a unit standard deviation.
The numbers of trainable parameters are recorded in the second column of Table~\ref{tab:gmwb_arch}.
We observe that the three \gls{dnn} metamodels have orders of magnitudes more trainable parameters than the two traditional regression metamodels.
Following the convention in machine learning literature, the three \gls{dnn} metamodels are said to have much higher \textit{model capacities}.
Treating regression metamodels as shallow neural networks, \gls{mlr} and \gls{qpr} are two neural networks with no hidden layer. 
For a traditional regression metamodel, the numbers of neurons in its input layer equals to the cardinality of its regression basis.
On the other hand, the three \gls{dnn} metamodels have several hidden layers and are more flexible than \gls{mlr} and \gls{qpr}.
Our \gls{fnn} has two hidden layers prior to its output layer.
Its hidden layers are feature extraction layers that transform the 240-dimension feature vector into a 32-dimension vector that can directly relate to the target variable.
This extraction process is automatic and does not require manual feature engineering.
Our \gls{rnn} and \gls{lstm} networks have three hidden layers.
They contain similar numbers of neurons as the \gls{fnn} but have deeper network structures.
For \gls{rnn}, two of its hidden layers are recurrent layers that capture the temporal dependency in the feature, and its last hidden layer is a standard feedforward layer that transforms the previous hidden states into a 32-dimension vector for target prediction.
Our \gls{lstm} has the same architecture as the \gls{rnn} but with \gls{lstm} cells in place of \gls{rnn} cells.
.

@@

For financial and actuarial applications, regulators and practitioners are often concerned about the robustness of \gls{dnn} models to noise in training labels, which hinders the adoption of these models in practice.
Since the true relationship is unknown in real-world applications, most deep learning literature illustrates the impact of noise by artificially injecting noise into real-world datasets, which is already noisy prior to the injection.
In our numerical experiments, we are able to use \gls{mc} simulation to generate a true dataset that approximates the true hedging losses with a high degree of precision, and, as a result, we are able to explore the important question of whether deep learning models are indeed capable of learning the true feature-label relationship from noisy training labels.
In this section, we treat the standard nested simulation procedure as a data generator and examine the noise tolerance of \gls{lstm} metamodels by varying the numbers of the outer scenarios ($M$) and the inner replications ($N$) used to generate the training samples.

@@

Our novel experiment design allows us to examine the impact of label noise on \gls{dnn} models.
We find that a \gls{dnn} with a suitable architecture is able to cut through the noise in training labels and learn the true complex dynamic hedging model.
By showcasing the resilience of these models, our study aims at encouraging regulatory bodies to recognize the value and applicability of deep learning metamodels in financial risk management, and it provides informed suggestions and guidance for the incorporation and oversight of advanced deep learning metamodel in \gls{mc} Simulation in financial applications.
Our findings are particularly insightful in this context.
